\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xfrac}
\usepackage{xcolor}

\newcommand{\tr}{^{\mathsf{T}}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\half}{\sfrac{1\!}2}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\interior}{int}
\DeclareMathOperator{\closure}{cl}
\DeclareMathOperator{\sgn}{sgn}

\DeclareFontFamily{U}{mathb}{\hyphenchar\font45}
\DeclareFontShape{U}{mathb}{m}{n}{
      <5> <6> <7> <8> <9> <10> gen * mathb
      <10.95> mathb10 <12> <14.4> <17.28> <20.74> <24.88> mathb12
      }{}
\DeclareSymbolFont{mathb}{U}{mathb}{m}{n}
\DeclareFontSubstitution{U}{mathb}{m}{n}
\let\dddot\relax
\DeclareMathAccent{\dddot}{0}{mathb}{"3B}

\setlist[enumerate, 1]{leftmargin=0pt, label=\textbf{\arabic*.}}

\begin{document}

\begin{enumerate}

\item \begin{enumerate}

\item \(\otimes^2V^*\) is a subspace of the vector space of functions \(V\times V\to\R\) equipped with pointwise addition. To see this note the identity element \(0_{\otimes^2V^*}(x)\coloneqq0\) is clearly a bilinear form, the sum of two bilinear forms is a bilinear form since
\begin{align*}
&(R+S)(au+v,w)\\
={}&R(au+v,w)+S(au+v,w)\\
={}&aR(u,w)+R(v,w)+aS(u,w)+S(v,w)\\
={}&a(R+S)(u,w)+(R+S)(v,w),
\end{align*}
and the negation of a bilinear form is a bilinear form since
\begin{align*}
&(-R)(au+v,w)\\
={}&-R(au+v,w)\\
={}&-aR(u,w)-R(v,w)\\
={}&a(-R)(u,w)+(-R)(v,w).
\end{align*}

\item Clearly \(0_{\otimes^2V^*}\) is symmetric. The sum of two symmetric bilinear forms is symmetric since
\begin{align*}
&(R+S)(u,v)\\
={}&R(u,v)+S(u,v)\\
={}&R(v,u)+S(v,u)\\
={}&(R+S)(v,u).
\end{align*}
The negation of a symmetric bilinear form is symmetric since
\begin{align*}
&(-R)(u,v)\\
={}&-R(u,v)\\
={}&-R(v,u)\\
={}&(-R)(v,u).
\end{align*}
Hence symmetric bilinear forms are a subspace of \(\otimes^2V^*\).

\item Clearly \(\Lambda^2V^*\cap S^2V^*=\{0\}\). Let \(T\in\otimes^2V^*\). Define
\begin{gather*}
K(v,u)\coloneqq\half\big(T(u,v)-T(v,u)\big)\\
H(u,v)\coloneqq\half\big(T(u,v)+T(v,u)\big)
\end{gather*}
Then \(T=K+H\) and \(K\in\Lambda^2V^*\) and \(H\in S^2V^*\), so \(\otimes^2V^*=\Lambda^2V^*+S^2V^*\) and hence \(\otimes^2V^*=\Lambda^2V^*\oplus S^2V^*\).

\item Let \(\{e_1,e_2\}\) be a basis for \(V\). Define the bilinear form
\[K(ae_1+be_2,ce_1+de_2)\coloneqq ad-bc.\]
Let \(T\in\Lambda^2V^*\). Let \(ae_1+be_2,ce_1+de_2\in V\). Then by bilinearity
\begin{align*}
&T(ae_1+be_2,ce_1+de_2)\\
&\quad=ac\cdot T(e_1,e_1)+ad\cdot T(e_1,e_2)+bc\cdot T(e_2,e_1)+bd\cdot T(e_2,e_2).
\end{align*}
But \(T\) is skew so \(T(e_1,e_1)=T(e_2,e_2)=0\) and \(T(e_1,e_2)=-T(e_2,e_1)\), and \(T\) simplifies to
\[T(ae_1+be_2,ce_1+de_2)=(ad-bc)T(e_1,e_2).\]
Hence \(T\) is a constant multiple of \(K\) and so \(\dim(\Lambda^2V^*)=1\).
\item Let \(T\in\otimes^2V^*\). By bilinearity \(T\) is completely determined by its values for
\begin{gather*}
a\coloneqq T(e_1,e_1),\quad b\coloneqq T(e_1,e_2)\\
c\coloneqq T(e_2,e_1),\quad d\coloneqq T(e_2,e_2).
\end{gather*}
Let
\[R=a(E^1\otimes E^1)+b(E^1\otimes E^2)+c(E^2\otimes E^1)+d(E^2\otimes E^2).\]
Then \(R\) agrees with \(T\) on the pairs \((e_i,e_j)\), so \(R=T\) and hence the \(E^i\otimes E^j\) span \(\otimes^2V^*\). Therefore the \(E^i\otimes E^j\) form a basis for \(\otimes^2V^*\) and \(\dim(\otimes^2V^*)=4\).

\end{enumerate}

\item \begin{enumerate}

\item We have
\[\dot c(t)=(2t,3t^2)\]
and hence on \(\R\setminus\{0\}\) we have
\begin{align*}
e_1(t)&=\frac1{\sqrt{4t^2+9t^4}}\begin{pmatrix}2t\\3t^2\end{pmatrix}\\
e_2(t)&=\frac1{\sqrt{4t^2+9t^4}}\begin{pmatrix}-3t^2\\2t\end{pmatrix}.
\end{align*}
Note
\[e_1(t)=\frac1{\sqrt{4+9t^2}}\begin{pmatrix}2\sgn t\\3\abs{t}\end{pmatrix}.\]
But there's no possible value that makes \(\sgn t\) continuous on \(\R\), so there cannot be a distinguished Frenet frame for \(c\) on all of \(\R\).

\item Note
\begin{align*}
\dot c(t)&=\abs{\dot c(t)}e_1(t)\\
\ddot c(t)&=D\big[\abs{\dot c(t)}\big]e_1(t)+\abs{\dot c(t)}\dot e_1(t)\\
&=D\big[\abs{\dot c(t)}\big]e_1(t)+\abs{\dot c(t)}^2\kappa(t)e_2(t)
\end{align*}
so
\[\det(\dot c(t),\ddot c(t))=\abs{\dot c(t)}^3\kappa(t)\]
and hence
\[\kappa(t)=\frac{\det(\dot c(t),\ddot c(t))}{\abs{\dot c(t)}^3}.\]

\item We have
\begin{align*}
c(t)&=(t^2,t^3)\\
\dot c(t)&=(2t,3t^2)\\
\ddot c(t)&=(2,6t)
\end{align*}
so
\begin{align*}
\kappa(t)&=\frac{\det(\dot c(t),\ddot c(t))}{\abs{\dot c(t)}^3}\\
&=\frac{12t^2-6t^2}{((2t)^2+(3t^2)^2)^{\sfrac{3\!}2}}\\
&=\frac{6}{\abs{t}(4+9t^2)^{\sfrac{3\!}2}}
\end{align*}

\end{enumerate}

\item Denote by \(o_i\) some vector in the span of \(e_1(t),\dots,e_i(t)\). We have
\begin{align*}
\dot c(t)&=\abs{\dot c(t)}e_1(t)\\
\ddot c(t)&=\abs{\dot c(t)}\dot e_1(t)+o_1=\abs{\dot c(t)}^2\kappa(t)e_2(t)+o_1\\
\dddot c(t)&=\abs{\dot c(t)}^2\kappa(t)\dot e_2(t)+o_2=\abs{\dot c(t)}^3\kappa(t)\tau(t)e_3(t)+o_2.
\end{align*}
and thus
\begin{align*}
\abs{\dot c(t)\times\ddot c(t)}&=\abs{\dot c(t)}^3\kappa(t)\\
\det(\dot c(t),\ddot c(t),\dddot c(t))&=\abs{\dot c(t)}^6\kappa(t)^2\tau(t).
\end{align*}
Hence
\begin{gather*}
\kappa(t)=\frac{\abs{\dot c(t)\times\ddot c(t)}}{\abs{\dot c(t)}^3}\\
\tau(t)=\frac{\det(\dot c(t),\ddot c(t),\dddot c(t))}{\abs{\dot c(t)\times\ddot c(t)}^2}.
\end{gather*}

\item \begin{enumerate}

\item If \(v\) is a vector satisfying
\[\nabla_vg(x,x)=0\]
then
\begin{align*}
&\nabla_v\Big[-x_0^2+\sum_{i=1}^nx_i^2\Big]=0\\
\iff{}&-2x_0v_0+\sum_{i=1}^n2x_iv_i=0\\
\iff{}&\,\,g(x,v)=0
\end{align*}
and hence \(T_x\mathbb{H}^n\cong\{\,v\in\R^{1,n}\mid g(x,v)=0\,\}\).

Let
\begin{align*}
u_1&=\Big(\frac{x_1}{x_0},1,0,0,0,\dots\Big)\\
u_2&=\Big(\frac{x_2}{x_0},0,1,0,0,\dots\Big)\\
u_3&=\Big(\frac{x_3}{x_0},0,0,1,0,\dots\Big)\\
&\,\,\;\vdots
\end{align*}
Then \(g(x,u_i)=0\) for all \(1\leq i\leq n\) and the \(u_i\) are all linearly independent so they form a basis for \(T_x\mathbb H^n\).

\item Let \(x\in \mathbb H^n\). Let \(\hat v\) denote the vector \(v\) without the first coordinate. Let \(u\in T_x\mathbb H^n\). We have
\begin{gather*}
g(u,u)=-u_0^2+\abs{\hat u}^2\\
-x_0^2+\abs{\hat x}^2=g(x,x)=-1\\
-x_0u_0+\langle\hat x,\hat u\rangle=g(x,u)=0\\
x_0>0.
\end{gather*}
Cauchy--Schwarz gives
\begin{align*}
&\abs{\hat u}^2\abs{\hat x}^2\geq\langle\hat x,\hat u\rangle^2\\
\implies{}&\abs{\hat u}^2(x_0^2-1)\geq x_0^2u_0^2\\
\implies{}&\abs{\hat u}^2x_0^2\geq x_0^2u_0^2+\abs{\hat u}^2\\
\implies{}&(g(u,u)+u_0^2)x_0^2\geq x_0^2u_0^2+\abs{\hat u}^2\\
\implies{}&g(u,u)x_0^2\geq\abs{\hat u}^2\\
\implies{}&g(u,u)\geq0
\end{align*}
so \(h\) is positive-definite.

\end{enumerate}

\item Let \(t\in\R\) and \(u,v\in\R^n\). Since \(R(t)\) is a orthogonal transformation we have
\[R(t)u\cdot R(t)v=u\cdot v.\]
Differentiating both sides gives
\[\dot R(t)u\cdot R(t)v+R(t)u\cdot\dot R(t)v=0\]
and so since \(R(0)=\text{id}_{\R^n}\) we have
\[\dot R(t)u\cdot v+u\cdot\dot R(t)v=0\]

\item Let \(A:\R^n\to\R^n\) be an isometry that preserves the origin. \(A\) then also preserves the norm. Let \(u,v\in\R^n\). Expanding \(\abs{u+v}^2\) gives
\[2\langle u,v\rangle=\abs{u+v}^2-\abs{u}^2+\abs{v}^2.\]
Hence \(A\) also preserves the dot product. Let \(a\in\R\). Then
\begin{align*}
&\abs{A(au+v)-aAu-Av}^2\\
={}&\abs{A(au+v)}^2\\
&-2\langle A(au+v),aAu\rangle\\
&-2\langle A(au+v),Av\rangle\\
&+\abs{aAu}^2\\
&-2\langle aAu,Av\rangle\\
&+\abs{Av}^2\\
={}&\abs{(au+v)}^2\\
&-2\langle (au+v),au\rangle\\
&-2\langle (au+v),v\rangle\\
&+\abs{au}^2\\
&-2\langle au,v\rangle\\
&+\abs{v}^2\\
={}&\abs{(au+v)-au-v}^2\\
={}&0.
\end{align*}
So \(A(au+v)=aAu+Av\) and thus \(A\) is linear and hence an orthogonal transformation. Let \(T\) be translation by \(B0\). The usual metric on \(\R^n\) is translation-invariant so \(R\coloneqq T^{-1}\circ B\) is an isometry that preserves the origin. It is therefore an orthogonal transformation and so we have
\[B=T\circ R\]
as desired.


\end{enumerate}

\end{document}